---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canvasser

<!-- badges: start -->
<!-- badges: end -->

The goal of canvasser is to make it easier for students to scrape their gradebook from canvas into a tibble to use as a dataset. Canvasser also allows students to calculate the weight of each category and what they need on the final for a desired grade.

## Installation

You can install the released version of canvasser from [CRAN](https://CRAN.R-project.org) with: 

``` r
install.packages("canvasser")
```

And the development version from [GitHub](https://github.com/) with: https://github.com/Brandontat5/canvasser

``` r
# install.packages("devtools")
devtools::install_github("Brandontat5/canvassser")
```
## Example - Getting assignment names

This is how to scrape the html file for assignment names:

```{r example 1}
library(canvasser)
scrape_asgns("./dev/csc225.html")
```

## Example - Getting assignment grades

This is how to scrape the html file for assignment grades:

```{r example 2}
library(canvasser)
scrape_asgn_grades("./dev/csc225.html")
```

## Example - Getting assignment max points possible

This is how to scrape the html file for assignment point totals:

```{r example 3}
library(canvasser)
scrape_total_points("./dev/csc225.html")
```

## Example - Scraping the gradebook

This is how to scrape the html for the entire dataset:

```{r example 4}
library(canvasser)
scrape_html_for_grades("./dev/csc225.html")
```


## Example - Calculating weight of each category in the gradebook

This is how to use the output of scrape_html_for_grades() in another function:

```{r example 5}
library(canvasser)
table <- scrape_html_for_grades("./dev/csc225.html")
calc_grade_per_category(table)
```
